\demes: a pain-free specification for complex demography

### 2021-06-14 paper.tex
Tidy up table.

\documentclass[11pt]{article}
\usepackage[round,comma,authoryear]{natbib}
\usepackage{fullpage}
\usepackage{authblk}
\usepackage{graphicx}

@@

\section*{Extensions and future directions}

\subsection*{Software support for \demes}
\aprcomment{at time of publication. TBD...}
\begin{itemize}
    \item \msprime: coalescent simulation \citep{kelleher2016efficient}
    \item \stdpopsim: a collection of maintained species and demographic models,
        which includes a large number of models specified using \demes
        \citep{adrion2020community}
    \item \fwdpy: forward-time Wright-Fisher simulation \citep{thornton2014c++}
    \item \moments: compute expected diversity statistics (SFS, LD) and perform
        demographic inference using summary statistics
        \citep{jouganous2017inferring,ragsdale2019models}
    \item \dadi: compute the expected SFS and perform demographic inference using
        summary statistics \citep{gutenkunst2009inferring}
\end{itemize}

@@

\section*{Appendix}

\aprcomment{Perhaps and example of a many-population model, and API to simulate using
\msprime, \fwdpy, and \moments?}

>>>>

\documentclass[11pt]{article}
\usepackage[round,comma,authoryear]{natbib}
\usepackage{fullpage}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{booktabs}

@@

% Add a bit more space between rows.
\renewcommand{\arraystretch}{1.5}
\begin{table}
\begin{center}
\begin{tabular}{lp{12cm}}
\toprule
\multicolumn{2}{l}{Software infrastructure}\\
\midrule
\texttt{demes-python} &
    A Python library for loading, saving, and working with
    Demes models. Includes conversion utilities for existing formats
    demographic model descriptions such as
    \texttt{ms}~\citep{hudson2002generating}.\\

\texttt{demes-c} &
    A C library for parsing Demes YAML descriptions.
    (\url{https://github.com/grahamgower/demes-c.git}). \\

\texttt{demesdraw} &
    A Python library for visualising Demes models
    (\url{https://github.com/grahamgower/demesdraw.git}). \\

\midrule
\multicolumn{2}{l}{Methods using Demes as input/output format}\\
\midrule

% TOOL AUTHORS: please add a row to this table to summarise what the software
% does, and how it implements demes.

\dadi &
    Summary of what dadi does and how it implements Demes~\citep{gutenkunst2009inferring}.
    \\

\fwdpy &
    Forward-time Wright-Fisher simulation \citep{thornton2014c++}\\

\gadma &
    Demographic inference \citep{noskova2020gadma}.\\

\moments &
    Compute expected diversity statistics (SFS, LD) and perform
    demographic inference using summary statistics
    \citep{jouganous2017inferring,ragsdale2019models}.\\

\msprime &
    Coalescent simulation of Demes models, including command line
    interface~\citep{kelleher2016efficient,kelleher2020coalescent}.\\

\stdpopsim &
    A collection of community empirical data for species
    and demographic models specified in Demes
    format~\citep{adrion2020community}.\\

\bottomrule
\end{tabular}
\end{center}
\caption{Software support for Demes. We have included software infrastructure developed
for working with Demes models (parsing, validation, visualisation, etc)
as well as all known downstream software that implements the specification,
at the time of writing.}
\end{table}

@@
